Practical Machine Learning Project By RRK
========================================================

Read the data files into pmlTraining and pmlTesting:
```{r}
setwd("~/Box Sync/Coursera/PracticalMachineLearning/project")
pmlTraining<-read.csv("pml-training.csv") 
pmlTesting<-read.csv("pml-testing.csv") 

```

Clean the data from columns that have more than 19,000 NA
```{r}
#training
pmlIsNATraining<-is.na(pmlTraining)
arrSumNATraining<-apply(pmlIsNATraining,2,sum) #for each column, how many are NA
bIsNAColumnTraining<-(arrSumNATraining>19000)
pmlTrainingClean<-pmlTraining[,!bIsNAColumnTraining]
#testing
pmlTestingClean<-pmlTesting[,!bIsNAColumnTraining]
```

Clean the data from columns that have more than 19,000 ""
```{r}
#training
pmlEmptyTraining<-pmlTrainingClean==""
arrSumEmptyTraining<-apply(pmlEmptyTraining,2,sum)
bIsEmptyColumnTraining<-(arrSumEmptyTraining>19000)
pmlTrainingClean<-pmlTrainingClean[,!bIsEmptyColumnTraining]
#testing
pmlTestingClean<-pmlTestingClean[,!bIsEmptyColumnTraining]
```
After clearning the data, 60 variables remained:
```{r}
names(pmlTrainingClean)
names(pmlTestingClean)
```

Split the training data to training and testingCV (testing cross validation)
```{r}
library(caret)
library(AppliedPredictiveModeling)
library(ggplot2)
inTrain = createDataPartition(pmlTrainingClean$classe, p = 3/4,list=FALSE)
training = pmlTrainingClean[ inTrain,]
testingCV = pmlTrainingClean[-inTrain,]
```

Train the training data with glm
```{r}
modelFit<-train(classe ~., data=training, method="rpart")
library(rattle)
fancyRpartPlot(modelFit$finalModel)
```

Make a prediction for the testingCV dataset
```{r}
confusionMatrix(testingCV[,60],predict(modelFit, newdata=testingCV))
```



```{r}

```
