#Practical Machine Learning Project
========================================================

##Background 
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). 

##Data
The training data for this project are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment. 

##Analysis
Read the data files into pmlTraining and pmlTesting:
```{r}
setwd("~/Box Sync/Coursera/PracticalMachineLearning/project")
pmlTraining<-read.csv("pml-training.csv") 
pmlTesting<-read.csv("pml-testing.csv") 

```

Clean the data from columns that have more than 19,000 NA
```{r}
#training
pmlIsNATraining<-is.na(pmlTraining)
arrSumNATraining<-apply(pmlIsNATraining,2,sum) #for each column, how many are NA
bIsNAColumnTraining<-(arrSumNATraining>19000)
pmlTrainingClean<-pmlTraining[,!bIsNAColumnTraining]
#testing
pmlTestingClean<-pmlTesting[,!bIsNAColumnTraining]
```

Clean the data from columns that have more than 19,000 ""
```{r}
#training
pmlEmptyTraining<-pmlTrainingClean==""
arrSumEmptyTraining<-apply(pmlEmptyTraining,2,sum)
bIsEmptyColumnTraining<-(arrSumEmptyTraining>19000)
pmlTrainingClean<-pmlTrainingClean[,!bIsEmptyColumnTraining]
#testing
pmlTestingClean<-pmlTestingClean[,!bIsEmptyColumnTraining]
```
After clearning the data, 60 variables remained:
```{r}
names(pmlTrainingClean)
names(pmlTestingClean)
```

Remove the var X as it perfectly correlate to the outcome
```{r}
pmlTrainingClean<-pmlTrainingClean[,-1]
pmlTestingClean<-pmlTestingClean[,-1]
```


Split the training data to training and testingCV (testing cross validation)
```{r}
library(caret)
library(AppliedPredictiveModeling)
library(ggplot2)
inTrain = createDataPartition(pmlTrainingClean$classe, p = 3/4,list=FALSE)
training = pmlTrainingClean[ inTrain,]
testingCV = pmlTrainingClean[-inTrain,]
```

Train the training data with rpart
```{r}
modelFit<-train(classe ~., data=training, method="rpart")
library(rattle)
fancyRpartPlot(modelFit$finalModel)
```

Make a prediction for the testingCV dataset with rpart
```{r}
confusionMatrix(testingCV[,59],predict(modelFit, newdata=testingCV))
```


Train the training data with random forest and make a prediction for testingCV dataset
```{r}
modelFit<-train(classe ~., data=training, method="rf")
summary(modelFit)
varImp(modFit)
confusionMatrix(testingCV[,59],predict(modelFit, newdata=testingCV))
```

##Predictions
Make prediction for the 20 items test set. Given the accuracy in the cross validation test, the predicted accuracy in the test set is very close to 100%
```{r}
answers<-predict(modelFit,newdata=pmlTestingClean)
```
Write files for submission
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(answers)
```